---
title: "Report"
author: "Koustubh Dwivedy, Pratik Acharya"
date: "December 16, 2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r user_space, include=FALSE}
# Before running this code, install "quantmod" and "xts"
# Before running this code, create a directory 

##############
# USER SPACE #
##############

# tick: Ticker of stock
tick = "AMZN"
# start date in yyyy-mm-dd format
date_start = "2010-12-31"
# end date in yyyy-mm-dd format
date_end = "2011-06-30"
# your working directory
dir = "C:/Users/TradingLab15/Desktop/R_project/report"
# web source from where to download data ("yahoo" or "google")
web_source = "google"

##################
# USER SPACE END #
##################
```

```{r core_code, include=FALSE}
setwd(dir)
library(PerformanceAnalytics)
library(quantmod)
library(xts)

# The following command gets data from Yahoo Finance (default)
data.CPNY<-getSymbols(tick, from=date_start, to=date_end, auto.assign=FALSE, src = web_source)

if(web_source == "google"){
	data.CPNY$CPNY.Adjusted<-data.CPNY[,4]
}

names(data.CPNY)<-paste(c("CPNY.Open","CPNY.High","CPNY.Low","CPNY.Close","CPNY.Volume","CPNY.Adjusted"))

#considering only the closing price in another variable
CPNY.prc.ret<-data.CPNY[,4]
CPNY.prc.ret[c(1:3,nrow(CPNY.prc.ret)),]

#calculating the price return in the same variable *.prc.ret
CPNY.prc.ret$CPNY.prc.ret<-Delt(CPNY.prc.ret$CPNY.Close)
CPNY.prc.ret[c(1:3,nrow(CPNY.prc.ret)),]
options(digit=7)

#calculating total returns
CPNY.ret<-data.CPNY[,6]
CPNY.ret[c(1:3,nrow(CPNY.ret)),]

CPNY.ret$CPNY.tot.ret=Delt(CPNY.ret$CPNY.Adjusted)
CPNY.ret<-CPNY.ret[,2]
CPNY.ret[c(1:3,nrow(CPNY.ret)),]

#calculating log returns
options(digits=3)
CPNY.log.ret<-data.CPNY[,6]
CPNY.log.ret$CPNY.log.ret<-diff(log(CPNY.log.ret$CPNY.Adjusted))
CPNY.log.ret[c(1:3,nrow(CPNY.log.ret)),]
CPNY.log.ret<-CPNY.log.ret[,2]
options(digits=7)

#comparing log and arithmetic returns
options(digits=3,CPNYpen=100)
tot.rets<-cbind(CPNY.ret,CPNY.log.ret)
tot.rets[c(1:3,nrow(tot.rets)),]
max(abs(tot.rets$CPNY.tot.ret-tot.rets$CPNY.log.ret),na.rm=TRUE)
min(abs(tot.rets$CPNY.tot.ret-tot.rets$CPNY.log.ret),na.rm=TRUE)
options(digits=7,CPNYpen=0)

#cumulating arithmetic returns
CPNY.acum<-CPNY.ret
CPNY.acum[1,1]<-0
CPNY.acum[c(1:3,nrow(CPNY.acum)),]

CPNY.acum$GrossRet<-1+CPNY.acum$CPNY.tot.ret
CPNY.acum[c(1:3,nrow(CPNY.acum)),]

CPNY.acum$GrossCum<-cumprod(CPNY.acum$GrossRet)
CPNY.acum[c(1:3,nrow(CPNY.acum)),]

CPNY.acum$NetCum<-CPNY.acum$GrossCum-1
CPNY.acum[c(1:3,nrow(CPNY.acum)),]

#cumulative log returns
CPNY.logcum<-CPNY.log.ret
CPNY.logcum[1,1]<-0
CPNY.logcum[c(1:3,nrow(CPNY.logcum)),]

logcumret=sum(CPNY.logcum$CPNY.log.ret)
logcumret

cumret=exp(logcumret)-1
cumret

#comparing price return and total return
CPNY.Ret<-cbind(CPNY.prc.ret,CPNY.ret)
CPNY.Ret[c(1:3,nrow(CPNY.Ret)),]

names(CPNY.Ret)<-c("Close","prc.ret","tot.ret")
CPNY.Ret[c(1:3,nrow(CPNY.Ret)),]

CPNY.Ret$prc.ret[1]<-0
CPNY.Ret$tot.ret[1]<-0
CPNY.Ret[c(1:3,nrow(CPNY.Ret)),]

CPNY.Ret$gross.prc<-1+CPNY.Ret$prc.ret
CPNY.Ret$gross.tot<-1+CPNY.Ret$tot.ret
CPNY.Ret[c(1:3,nrow(CPNY.Ret)),]

CPNY.Ret$cum.prc<-cumprod(CPNY.Ret$gross.prc)
CPNY.Ret$cum.tot<-cumprod(CPNY.Ret$gross.tot)
CPNY.Ret[c(1:3,nrow(CPNY.Ret)),]

#WEEKLY returns
wk<-data.CPNY
wk[c(1:3,nrow(data.CPNY)),]

CPNY.weekly<-to.weekly(wk)
CPNY.weekly[c(1:3,nrow(CPNY.weekly)),]

CPNY.weekly<-CPNY.weekly[,6]
CPNY.weekly[c(1:3,nrow(CPNY.weekly)),]

CPNY.weekly$Ret<-Delt(CPNY.weekly$wk.Adjusted)
CPNY.weekly[c(1:3,nrow(CPNY.weekly)),]

CPNY.weekly<-CPNY.weekly[-1,2]
CPNY.weekly[c(1:3,nrow(CPNY.weekly)),]

CPNY.acum[c(6,11,15),]

#MONTHLY returns
mo<-data.CPNY
mo[c(1:3,nrow(data.CPNY)),]

CPNY.monthly<-to.monthly(mo)
CPNY.monthly[c(1:3,nrow(CPNY.monthly)),]

CPNY.monthly<-CPNY.monthly[,6]
CPNY.monthly[c(1:3,nrow(CPNY.monthly)),]

CPNY.monthly$Ret<-Delt(CPNY.monthly$mo.Adjusted)
CPNY.monthly[c(1:3,nrow(CPNY.monthly)),]

CPNY.monthly<-CPNY.monthly[-1,2]
CPNY.monthly[c(1:3,nrow(CPNY.monthly)),]


### Drawdowns
SP<-data.CPNY$CPNY.Adjusted
DJ.roc<-ROC(SP,n=1,type="discrete")
Drawdowns<-table.Drawdowns(DJ.roc[,1])
```


# Company Report `r tick`
Data Source: `r web_source` finance

## Price Returns
The dollar change based solely on the closing price of a security is called capital gains and the percentage price in the closing price of a security is its price return. The price return is measured over some investment horizon (e.g., 1 day, 1 month, 1 year, etc.). The length of the period depends on the application, but the return calculations should be consistent such that cumulating all the 1-day returns in a given year should equal the annual return.

## Total Returns
The return to investors from holding shares of stock are not limited to changes in the price of the security. For companies that pay dividends, the shareholders holding shares prior to the ex-dividend date receive cash payments that they are able to
reinvest. In fact, automatically reinvesting dividends may be an option for some securities. Therefore, the total return a shareholder can receive from a stock that pays dividends includes both the change in the price of the shares she owns as well
as any income generated from the dividends and the reinvestment of those dividends on the ex-date. This is known as the holding period return or total return.


```{r, echo=FALSE}
y.range<-range(CPNY.Ret[,5:6])
plot(CPNY.Ret$cum.tot, type="l",auto.grid=FALSE,xlab="Date",ylab="Value of Investment ($)",ylim=y.range,minor.ticks=FALSE, main="Stock Performance Based On Total Returns and Price Returns")
lines(CPNY.Ret$cum.prc, type="l",lty=3)
abline(h=1,col="black")
legend("topleft",col=c("black","black"),lty=c(1,3),c("Value Based on Total Return","Value Based on Price Return"))
```

## Airthmetic Cumulative Returns

```{r, echo=FALSE, warning=FALSE}
CPNY.acum$NetCum[dim(CPNY.acum$NetCum)[1]]
```

This means that an investment made in `r tick` stock on `r date_start` would have returned `r CPNY.acum$NetCum[dim(CPNY.acum$NetCum)[1]]*100`% by the end of `r date_end`.

## Logarithmic Cumulative Returns
```{r, echo=FALSE}
logcumret
```

## Logarithmic Total Returns
[Lograthmic Return](https://en.wikipedia.org/wiki/Rate_of_return#Logarithmic_or_continuously_compounded_return)


```{r, echo=FALSE}
y.range<-range(CPNY.logcum[,1])
plot(CPNY.logcum, type="l",auto.grid=FALSE,xlab="Date",ylab="Logarithmic Total Returns", ylim=y.range,minor.ticks=FALSE, main=tick)
```


## Weekly Returns
```{r, echo=FALSE}
y.range<-range(CPNY.weekly[,1])
plot(CPNY.weekly, type="l",auto.grid=FALSE,xlab="Date",ylab="Weekly Returns", ylim=y.range,minor.ticks=FALSE, main=tick)
```
```{r, echo=FALSE}
CPNY.weekly
```

## Monthly Returns
```{r, echo=FALSE}
y.range<-range(CPNY.monthly[,1])
plot(CPNY.monthly, type="l",auto.grid=FALSE,xlab="Date",ylab="Monthly Returns", ylim=y.range,minor.ticks=FALSE, main=tick)
```
```{r, echo=FALSE}
CPNY.monthly
```

## Drawdowns
```{r, echo=FALSE}
Drawdowns[order(as.Date(Drawdowns$From, format="%y/%m/%d")),]
```